---
title: "Project1- CITS5507 - Fish School Behavior"
author: "Long Qin(23829101)  Haitian Wang(23815631)"
date: "2023-09-25"
output: html_document
---

# Experiment 1
## 1.1
```{r}

# Load the necessary libraries if you haven't already
library(ggplot2)
library(dplyr)

# Read the "static" and "dynamic" datasets
data_HPC_S <- read.table("C:/Users/qinlo/OneDrive/Desktop/4009_Computational_Data_Analysis/static_setonix.tsv", header = TRUE)
data_HPC_D <- read.table("C:/Users/qinlo/OneDrive/Desktop/4009_Computational_Data_Analysis/dynamic_setonix.tsv", header = TRUE)

# Read the "guided" dataset
data_HPC_G <- read.table("C:/Users/qinlo/OneDrive/Desktop/4009_Computational_Data_Analysis/guided_setonix.tsv", header = TRUE)

# Add a column to indicate the source of the data
data_HPC_S$Source <- "Static"
data_HPC_D$Source <- "Dynamic"
data_HPC_G$Source <- "Guided"

# Combine the datasets into one
combined_data <- bind_rows(data_HPC_S, data_HPC_D, data_HPC_G)

# Group the combined data by Num_Threads and Source, and calculate the average Total_Time for each group
thread_averages <- combined_data %>%
  group_by(Num_Threads, Source) %>%
  summarize(Avg_Total_Time = mean(Total_Time))

# Create a plot to visualize the combined data
ggplot(thread_averages, aes(x = Num_Threads, y = Avg_Total_Time, color = Source)) +
  geom_line(size = 0.7) +
  geom_point(size = 0.9, fill = "white", shape = 21, alpha = 2) +
  labs(x = "Number of Threads", y = "Average Total Time",
       title = "Total Time vs. Threads (Static vs. Dynamic vs. Guided)",
       subtitle = "Performance Analysis",
       caption = "Data Source files: static_setonix.tsv, dynamic_setonix.tsv, guided_setonix.tsv") +
  theme_minimal() +
  theme(legend.position = "top",  # Position the legend at the top
        plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(hjust = 0),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"),
        panel.border = element_blank()) +
  scale_x_continuous(breaks = c(0, 25, 50, 100, 200)) +  # Specify the x-axis breaks
  scale_y_continuous(breaks = c(0, 2, 5, 10, 13))

```
# 1.2

```{r}
# Create a plot to visualize the combined data, focusing on x < 25
ggplot(thread_averages, aes(x = Num_Threads, y = Avg_Total_Time, color = Source)) +
  geom_line(size = 0.7) +
  geom_point(size = 0.9, fill = "white", shape = 21, alpha = 0.7) +
  labs(x = "Number of Threads", y = "Average Total Time",
       title = "Total Time vs. Threads (Static vs. Dynamic vs. Guided)",
       subtitle = "Details - Threads less than 20",
       caption = "Data Source files: static_setonix.tsv   dynamic_setonix.tsv") +
  theme_minimal() +
  theme(legend.position = "top",
        plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(hjust = 0),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"),
        panel.border = element_blank()) +
  scale_x_continuous(breaks = c(0, 5, 10,15, 20)) +  # Specify the x-axis breaks
  scale_y_continuous(breaks = c(0, 5, 10, 13)) +
  coord_cartesian(xlim = c(0, 20))  # Set x-axis limits to focus on x < 25


```

# 1.3

```{r}
library(ggplot2)
library(dplyr)

# Read the CSV file
data_ReductionCritical <- read.csv("C:/Users/qinlo/OneDrive/Desktop/4009_Computational_Data_Analysis/Reduction_Critical.csv")

# Create a plot with improved aesthetics
plot <- ggplot(data_ReductionCritical, aes(x = Threads, y = Runtime, color = Construct)) +
  geom_point(size = 3) + # Increase point size
  geom_line(size = 1, linetype = "solid") + # Solid lines connecting points
  scale_x_log10() +
  labs(x = "Threads - log10", y = "PerformanceTime", title = "PerformanceTime vs. Threads by Construct") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

# Print the improved plot
print(plot)

```


# Experiment 2


```{r}
# ...
# ...```{r}
# Load the necessary libraries if you haven't already
library(ggplot2)
library(dplyr)

# Read the CSV file
data_strategy <- read.csv("C:/Users/qinlo/OneDrive/Desktop/4009_Computational_Data_Analysis/strategies.csv")

# Filter the data for the "runtime" category
runtime_data <- data_strategy %>%
  filter(Schedule == "runtime" & Threads %in% c(2, 4, 8))

# Define custom color and linetype palettes for schedules
color_palette <- c("static" = "blue", "dynamic" = "red", "guided" = "green", "runtime" = "purple")
linetype_palette <- c("static" = "solid", "dynamic" = "dashed", "guided" = "dotdash", "runtime" = "dotted")

# Create individual line plots for each combination, faceted by Threads
plots <- data_strategy %>%
  ggplot(aes(x = Chunk, y = Runtime, color = Schedule, linetype = Schedule)) +
  geom_line(size = 0.8) +
  geom_hline(data = runtime_data, aes(yintercept = Runtime), linetype = "dotted", color = "purple", size = 1.5) + # Add horizontal lines for the "runtime" category with increased size and color
  labs(x = "Chunk Numbers", y = "PerformanceTime",
       title = "PerformanceTime vs. Chunk by Threads and Schedule",
       caption = "Data Source file: strategies.csv") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 15, face = "bold"),
    plot.caption = element_text(hjust = 0),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white"),
    plot.background = element_rect(fill = "white"),
    panel.border = element_blank(),
    legend.position = "top",
    legend.title = element_blank(),
    legend.key = element_blank(),
    legend.background = element_blank()
  ) +
  scale_color_manual(values = color_palette) +
  scale_y_log10() +
  scale_x_log10() +
  scale_linetype_manual(values = linetype_palette) +
  facet_wrap(~Threads, scales = "free_y", nrow = 3, labeller = labeller(Threads = c("2" = "2 Threads", "4" = "4 Threads", "8" = "8 Threads"))) # Change facet labels

print(plots)


```


# Experiment 3
## 3.1

```{r}
library(ggplot2)
# Data for reduction and critical sections
num_threads <- c(4, 6, 8, 10, 12, 14, 16)
reduction_times <- c(0.2, 0.173, 0.173, 0.142, 0.159, 0.13, 0.125)
critical_times <- c(8.532, 10.722, 13.908, 16.478, 17.206, 17.162, 15.167)

# Create data frames
reduction_data <- data.frame(Thread = num_threads, Time = reduction_times, Section = "Reduction")
critical_data <- data.frame(Thread = num_threads, Time = critical_times, Section = "Critical")

# Combine data frames
combined_data <- rbind(reduction_data, critical_data)

# Create the bar chart
ggplot(combined_data, aes(x = as.factor(Thread), y = Time, fill = Section)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Number of Threads", y = "PerformanceTime", title = "Comparison of Reduction vs. Critical Sections") +
  theme_minimal() +
  theme(legend.position = "top") +
  scale_fill_manual(values = c("Reduction" = "blue", "Critical" = "red"))

```


## 3.2

```{r}

# Assuming you have your data in a data frame called "data"
data <- read.table(text = "
construct    thread_num    total_time
critical2    4             264.935
critical2    6             309.856
critical2    8             343.083
critical2    10            376.624
critical2    12            403.853
critical2    14            392.836
critical2    16            359.991
reduction    4             50.24
critical1    4             126.418
reduction    6             57.839
critical1    6             171.52
reduction    8             52.911
critical1    8             207.754
reduction    10            34.267
critical1    10            218.854
reduction    12            47.591
critical1    12            210.014
reduction    14            46.249
critical1    14            195.282
reduction	   16	         	 44.437
critical1	   16		         192.251

", header = TRUE)

# Load the ggplot2 library
library(ggplot2)

# Create a bar plot
ggplot(data, aes(x = construct, y = total_time, fill = factor(thread_num))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Construct", y = "PerformanceTime", title = "Total Time by Construct and Thread Number") +
  scale_fill_discrete(name = "Thread Numbers") +
  theme_minimal()



```
